%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\definecolor{awesome}{HTML}{b30000}
%\colorlet{awesome}{awesome-HTML}

%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Akhilesh} \headerlastnamestyle{Devrari} \\
	\vspace{2mm}
	{\faEnvelope\ devrari.akhilesh@gmail.com} | {\faMobile\ 8126268021} | {\faMapMarker\ 113 B13 IIT Mandi 175005} | {\faLink\ \href{https://akhileshdevrari.github.io/}{akhileshdevrari.github.io}}
\end{center}

\vspace{1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{B. Tech in Computer Science and Engineering}
	{Indian Institute of Technology Mandi}
	{Himachal Pradesh, India}
	{August 2016 – June 2020}
	{CGPA: 8.50/10}
\end{cventries}

%\vspace{-2mm}

\cvsection{Skills}
\begin{cventries}
	\vspace{-4mm}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming:  & {\skill{ Comfortable: C/C++ \hspace{1cm} Familiar: Python, Javascript, Scala, Prolog, C\#, PHP}} \\
		\end{tabular}}}
	{}
	{}
	{}
	
	\vspace{-10mm}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
			Utilities:  & {\skill{ MySQL, Git, Linux shell utilities, HTML/CSS}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-10mm}
\cvsection{Achievements}
\begin{itemize}
	\item 1st place in Topcoder hackathon. Built a utility to perform online eye tests for distant vision and color vision.
	\item 94 rank  in ACM ICPC Amritapuri regionals. 118 rank in online qualifiers across India.
	\item All India Rank 1785  out of 1.2 million participants in JEE Advanced 2016.
	\item 1st place in Avishkar 2017 (Technical event of IIT Mandi) for remote home automation project.
\end{itemize}


%\vspace{-7mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{Interpreter}
	{Bird}
	{C++}
	{\href{https://github.com/akhileshdevrari/Bird}{github.com/akhileshdevrari/Bird}}
	{
		\vspace{-3mm}
		\begin{itemize}
			\item Created an interpreter for a simple programming language from scratch.
			\item Added support for arithmetic operators, conditional and loop statements.
		\end{itemize}		
	}
	
	\vspace{-5mm}
	\cventry
	{Practice platform for competitive programmers}
	{CodeGym}
	{PHP, MySQL}
	{\href{https://github.com/akhileshdevrari/codegym}{github.com/akhileshdevrari/codegym}}
	{
		\vspace{-3mm}
		\begin{itemize}
			\item Users could create custom programming contests, selecting topics and time limit and track their performance over time.
			\item Created as part of a course project and got an A grade.
		\end{itemize}
	}
	
	
	\vspace{-5mm}
	\cventry
	{Normalization tool}
	{Normie}
	{Javascript}
	{\href{https://github.com/akhileshdevrari/Normie}{github.com/akhileshdevrari/Normie}}
	{
		Created a normalization tool with the following features:
		\begin{itemize}
			\item Find minimal cover, closure, candidate keys and normal form of given schema.
			\item Added feature to find probable functional dependencies from uploaded TSV file and convert given schema to 3NF
		\end{itemize}
	}
	
	\vspace{-5mm}
	\cventry
	{Guitar tuner}
	{Rhythm}
	{Javascript}
	{\href{https://github.com/akhileshdevrari/Rhythm}{github.com/akhileshdevrari/Rhythm}}
	{
		\vspace{-3mm}
		\begin{itemize}
		\item Created a web app to tune a guitar in standard tuning using WebAudio API.
		\item Used Auto-correlation techniques to produce results good enough for amateur use.
		\end{itemize}	
	}
	
	\vspace{-5mm}
	\cventry
	{Bash-like shell}
	{BombShell}
	{C++}
	{\href{https://github.com/akhileshdevrari/BombShell}{github.com/akhileshdevrari/BombShell}}
	{
		\vspace{-3mm}
		\begin{itemize}
			\item Created a bash-like shell able to execute processes for linux from scratch.
			\item Added features for piping, IO redirection and command auto-complete.
		\end{itemize}	
	}
	
\end{cventries}


\vspace{-3mm}


%\cvsection{Coursework}
%\vspace{-5mm}
%\begin{cvhonors}
%	\begin{minipage}[t]{0.05\textwidth}
%		A\\
%		A\\
%		A\\
%		A
%	\end{minipage}\begin{minipage}[t]{0.45\textwidth}
%		 Data Structures and Algorithms\\	
%		 Applied Database Practicum\\	
%		 Linear Algebra\\	
%		 Probability, Statistics and Random Processes	
%	\end{minipage}\begin{minipage}[t]{0.05\textwidth}
%		A\\
%		i\\
%		i\\
%		i
%	\end{minipage}\begin{minipage}[t]{0.45\textwidth}
%		Mathematical Foundations of Computer Science\\
%		Communicating Distributed Processes\\
%		Artificial Intelligence\\	
%		Pattern Recognition\\	
%	\end{minipage}	
%
%\color[HTML]{b30000}
%\textit{A~:~~A~grade }
%\textit{i~~~:~~in~progress}  
%	
%\end{cvhonors}
%



\vspace{-2mm}




\cvsection{Miscellaneous}
\begin{itemize}
	\item Teaching Assistant in IC250 (Data Structures and Practicum) and IC252 (Data Science). 
	\item Interested in algorithms and competitive programming.
	\item \textbf{Coursework (with 9/10 or higher) :} Data structures and algorithms, Algorithm design and analysis, Artificial intelligence, Applied database practicum, Linear algebra, Probability and statistics, Communicating distributed processes, Mathematical foundations of computer science, Paradigms of programming
\end{itemize}



%This is to fit the document in one page :)
\vspace{-8mm}
\ 
\end{document}